Coherent optical creation of a single molecule

### 2020-12-09 paper.tex
one more subscript font

\begin{figure*}[htb]
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer power and detuning.
    (a) The Raman resonance~($\omega_{\rm R}$) fitted by $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_{\rm a}^2-\Omega_{\rm m}^2)/2$
    are the power ($P$) dependent background and $v'=0$ contributions
    to the light shift and
    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
    the $v'=0$ resonance frequency $f_0$.
    $a_P$ is fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_{\rm m}\gg\Omega_{\rm a}$} to obtain the Raman resonance frequency
    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
    (b) Raman Rabi frequency ($\Omega_{\rm R}$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_{\rm a}\Omega_{\rm m}/2$
    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_{\rm m}$ (top) and $\Omega_{\rm a}$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_{\rm m}$ and
    $P^{0.79}$ scaling of $\Omega_{\rm a}$.
    \label{f-det}}
\end{figure*}

>>>>

\begin{figure*}[htb]
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer power and detuning.
    (a) The Raman resonance~($\omega_{\rm R}$) fitted by $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_{\rm a}^2-\Omega_{\rm m}^2)/2$
    are the power ($P$) dependent background and $v'=0$ contributions
    to the light shift and
    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
    the $v'=0$ resonance frequency $f_0$.
    $a_P$ is fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_{\rm m}\gg\Omega_{\rm a}$} to obtain the Raman resonance frequency
    at zero tweezer power $\omega_{\rm R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
    (b) Raman Rabi frequency ($\Omega_{\rm R}$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_{\rm a}\Omega_{\rm m}/2$
    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_{\rm m}$ (top) and $\Omega_{\rm a}$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_{\rm m}$ and
    $P^{0.79}$ scaling of $\Omega_{\rm a}$.
    \label{f-det}}
\end{figure*}
